---
title: "hw2"
output: html_document
---

#Intermediate R

##Relational Operators

#### The greater string is determined based on alphabetical order
```{R}
"csx" <= "is awesome"
```

#### TRUE == 1, FALSE == 0
```{R}
TRUE == 1
```
```{R}
FALSE != 1
```
```{R}
TRUE > FALSE
```

#### The && and || operators returns the first element's logic output. 
```{R}

```
#### 胖虎的减肥大作战
![我要準備出道當歌手了，幫我減肥！
](C:/Users/Heidi Chen/Downloads/Fat_tiger.png)
+ 以下是營養師的七日飲食記錄的一部分，，來看看他一個禮拜喝可樂跟喝喝雪碧的次數。
(Creating a vector)
```{r}
coke <- c(1, 2, 1, 2, 1, 1.5, 2.5)
sprite <- c(3, 1, 2, 4, 3, 2, 1)
coke > sprite
```

```{r}
sodas <- matrix(c(coke, sprite), nrow = 2, byrow = TRUE)
```

#### The V2 looping is new to e. Utilising ':' in R is still very new for myself. 

#### Knowing how to properly use the break and next statements.

#### ?(function) will allow us to get help about functions

#### ... ellipsis is a way for R to pass arguments along without the fucntion having to name them explicitly. 

#### writing a function in R is also totally different from python. Setting default values to arguments are important to prevent running into an error. 

#### The passing arguments by values part, I am still uncertain. Need to relook again. 

#### using lapply to quickly pass list or vector through functions. Both built-in and your own functions. 
* Can return R objects of different classes
* Always store contents in a list.
* Can sometimes repeat homogeneous contents. 

#### sapply function
*Automatically simplify the output from a list to a vector
* but still returns a list if it cannot find a meaningful way to simplify the vector.

#### vapply function
* apply function over list or vector and specify the output. 

#### str function in R is short for structure, not a string, this is something that I'll have to watch out for. 

#### Regular expressions. Useful for data cleaning.

* Sequence of (meta)characters
* Pattern existence
* Pattern replacement
* Pattern extraction

#### Metacharacters
* ^a refers to elements starting with a
* a$ refers to elements ending with a 
?regex in the console

grepl outputs logic that matches the pattern
grep outputs the indices that matches the pattern
sub, subsitutes components of strings (the first match)
gsub substitutes all matches in the string. 

##Handling dates
* R uses POSIXct as time to do time manipulations
* Dedicated R packages includes lubridate, zoo and zts.