---
title: "hw2"
output: html_document
---

#Intermediate R

##Relational Operators

#### The greater string is determined based on alphabetical order
```{R}
"csx" <= "is awesome"
```

#### TRUE == 1, FALSE == 0
```{R}
TRUE == 1
```
```{R}
FALSE != 1
```
```{R}
TRUE > FALSE
```

#### The && and || operators returns the first element's logic output. 

#### 胖虎的减肥大作战  
![我要準備出道當歌手了，幫我減肥!
](C:/Users/Heidi Chen/Downloads/Fat_tiger.png)
+ 以下是營養師的七日飲食記錄的一部分，，來看看他一個禮拜喝可樂跟喝喝雪碧的次數。  
(Creating a vector)
```{r}
coke <- c(1, 2, 1, 2, 1, 1.5, 2.5)
sprite <- c(3, 1, 2, 4, 3, 2, 1)
coke > sprite
```

```{r}
sodas <- matrix(c(coke, sprite), nrow = 2, byrow = TRUE)
#When does soda equals 3?
sodas == 3
sodas <= 1
```

#### Break statements terminates the loop while the next statements skips part of the loop. 
```{r}
geniuses <- list("pecu", "cm", "miccwan")

for (genius in geniuses) {
  if(nchar(genius) == 2) {
    break
  }
  print(genius)
}
```

```{r}
for (genius in geniuses) {
  if(nchar(genius) == 2) {
    next
  }
  print(genius)
}

```

#### The v2 for loop enables us to access the index of the vector
```{r}
geniuses <- as.vector(geniuses)
for(i in 1:length(geniuses)) {
  print(paste(geniuses[i], "is on position",
              i, " in the geniuses vector"))
}
```

#### ... ellipsis is a way for R to pass arguments along without the fucntion having to name them explicitly. 

#### writing a function in R 
```{r}
I_am_awesome <- function (a) {
  print(paste(a," is not as awesome as I am"))
}
I_am_awesome("Chris Hemsworth")
```

#### R passes arguments by value, so values within the function does not affect the variable outside the function. 

```{r}
power <- function (x){
  x <- x ** x
  x
}

a <- 5
power(a)
##Though power(a) outputs a**a, variable remains unchanged. 
a
```


#### using lapply to quickly pass list or vector through functions. Both built-in and your own functions. 
* Can return R objects of different classes
* Always store contents in a list.
* Can sometimes repeat homogeneous contents. 

#### sapply function
* Automatically simplify the output from a list to a vector
* but still returns a list if it cannot find a meaningful way to simplify the vector.

#### vapply function
* apply function over list or vector and specify the output. 

 * The above three are ways we can run objects through functions without the need to do a for loop.
 
#### str function in R is short for structure, not a string

```{r}
str(a)
```
#### other useful functions includes
* Data Utilities: seq(), rep(), sort(), rev()
* Math Utilities: abs(), round(), sum()


#### Regular expressions. Useful for data cleaning.
```{r}
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "dalai.lama@peace.org", "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")
#using grepl to match for "edu
grepl("edu", emails)
grep("edu", emails)
#grepl returns a logic while grep returns the index.
```
  
sub, subsitutes components of strings (the first match)
gsub substitutes all matches in the string. 

#### Metacharacters
* ^a refers to elements starting with a
* a$ refers to elements ending with a 
?regex in the console

#### Handling dates
* R uses POSIXct as time to do time manipulations
* Dedicated R packages includes lubridate, zoo and zts.