---
title: "hw3_dataframes"
output: html_document
---

####Creating a data frame
```{r eval = FALSE}
data_frame_name <- data.frame(variable1, variable2)
data_frame_name <- as.data.frame(object,...)
```
####Looking at data
* dim()
* head()
* tail()
* str()
* summary()

####Adding data into dataframe
* Dollar sign
* cbind
```{r eval = FALSE}
data_frame_name <- cbind(data_frame_name, variable3)
```

####Removing data from dataframe
* Dollar sign
```{r eval = FALSE}
data_frame_name$variable1 <- NULL
```
* subset function
```{r eval = FALSE}
data_frame_name <- subset(data_frame_name, select = -variable1)
```

####Renaming column names
```{r eval = FALSE}
names(data_frame_name)[indexno.] <- "new_name"
```
####QUerying for specific cases with subset functions
```{r eval = FALSE}
subset(data_frame_name, conditions....|...&..)
```

####Adding new rows with rbind
* cbind for column bind, rbind for row bind.
```{r eval = FALSE}
data_frame_name <- rbind(data_frame_name, new_row)
```
####Summary statistics
```{r eval = FALSE}
summary(data_frame_name)
```

####Changing dataframes to wide or long.
```{r eval = FALSE}
#change to long method 1
data_frame_name_long <- data.frame(data_frame_name[, c(variable1, variable 2, variable 3)])

#change to long method 2
data_frame_name_long <- gather(data_frame_name_wide)

#change to wide method 1
data_frame_name_wide <- spread(data_frame_name_long, key = ..., value = ...)
```

####Merging dataframes
* Outer join and inner join
* Both outer and inner join
* Merging based on multiple variables. 