---
title: "hw4_Tidyverse"
output: html_document
---
libraries used:
```{r echo=T, results='hide'}
library(dplyr)
library(magrittr)
library(ggplot2)
```
#### Data manipulation techniques with filter, arrange, mutate.
```{r}
data("CO2") 

carbon <- CO2 %>%
  filter(., Treatment == "chilled") %>%
  #filter verb
  arrange(., desc(conc)) %>%
  #Arrange verb - sorts a table based on a variable, here we put it in descending order using desc().
  mutate(conc_per_t = conc / 100)
  #Mutate verb here enables us to add in another column called conc_per_t. Helps in computing new variables. 
```


####Plotting scatterplots with ggplot2
* using log scales  

####Aesthetics
* using colours to represent categorical values
* using size of the dots to represent some numerical significance. 
```{r}
ggplot(CO2, aes(x = Plant, y = uptake, color = Treatment, size = conc)) + geom_point()
```
#### Faceting
* adds another dimension to look at data. Good for time series. 
```{r}
ggplot(CO2, aes(x = Plant, y = uptake, color = Treatment, size = conc)) + geom_point() + facet_grid(~Type)
```
The data transformation and visualisation framework.

####summarize verb
summarize(mean variable = mean(variable))

####group_by verb
summarizing by groups
group_by(variable) - variable becomes the key of the output. 

####visualising summarised data
start y axis at zero = expand_limits(y = 0)

####different kinds of plots
* *geom_point()* refers to scatterplot
* *geom_line()* refers to lineplot
* *geom_col()* refers to barplot (barplots always start at 0)
* *geom_histogram(binwidth =...)* refers to histogram. Binwidth will determine the width of the bars.only contains 1 aesthetic
* *geom_boxplot()* refers to a boxplot