---
title: "TFIDF_PCA_Kmeans"
output: html_document
---
# Text mining using TF-IDF, PCA and K means
### Today we will be looking at the annual bill board winners to see if there are changes in the billboard winning songs from 1990 to 2018. 

1. _Load the libraries_
```{r loadlibraries, results = "hide"}
library(tm)
library(magrittr)
library(tidytext)
library(Matrix)
library(factoextra)
library(stringr)
library(readr)
library(tidyr)
```

```{r workingdirectory, include = FALSE}
setwd("~/GitHub/CSX_RProject_Summer_2018/week_3/songs_data")
```
2. _Load in the txt files_
```{r}
files_list <- list.files(path = ".", recursive = TRUE,
                         pattern = "*.txt$", full.names = TRUE)
songs <- lapply(files_list, read_file) %>%
  unlist(.)
```

3. _Change format into corpus_
```{r}
df <- as.data.frame(songs)
corpus_song <- Corpus(VectorSource(df$songs))
```

4. _Cleaning up some punctuations_
```{r}
song_words <- corpus_song %>%
  tm_map(removePunctuation)  %>%
  tm_map(removeNumbers)
```

5. _Document Term Matrix_
```{r}
dtm <- DocumentTermMatrix(song_words)
inspect(dtm)
```
6. Now that the text files are prepared, we will now move on to the analysis

### TF-IDF
1. _Tabulating the Term Frequencies_
```{r}
doc_tf <- apply(as.matrix(dtm), 2, function(word) {word/sum(word)})
```

2. _Create the IDF function to load the algorithm_
```{r}
idf <- function(doc) {
  return(log2( length(doc) + 1 / nnzero(doc)) )
}
```

3. _Obtain IDF_
```{r}
doc_idf <- apply(as.matrix(dtm), 1, idf)
```

4. _Obtain TFIDF_
```{r}
docs_tfidf <- doc_tf * doc_idf
```

### PCA
1. _Conduct the PCA using the tfidf results_
```{r}
docs_pca <- prcomp(docs_tfidf, scale = T)
```

2. _Drawing the plots with eigenvalues_
```{r}
fviz_eig(docs_pca)
fviz_pca_ind(docs_pca, geom.ind = c("point"), col.ind = "cos2")
fviz_pca_var(docs_pca, col.var = "contrib")
fviz_pca_biplot(docs_pca, geom.ind = "point")
```

3. _Save the individual PCA results into separate variables_
```{r}
docs_eig <- get_eig(docs_pca)
docs_var <- get_pca_var(docs_pca)
docs_ind <- get_pca_ind(docs_pca)
```

### K means clustering
1. _K means_
```{r}
ind_coord2 <- docs_ind$coord[,1:2]
wss <- c()
for (i in 1:10) {
  wss[i] <- kmeans(ind_coord2, i)$tot.withinss
}
plot(wss, type = "b")
```
2. _Clustering_
```{r}
km <- kmeans(ind_coord2, 3)
plot(ind_coord2, col = km$cluster)
points(km$centers, col = 1:3, pch = 8, cex = 2)
```

The dark blue point is a song called "Despacito", which is the hit song of last year. Due to the full Spanish nature of the song, I believe that that is the reason why it got singled out from the rest. 

The green point is Usher's Yea in 2004. I have no clue why in particular the lyrics are different. 

So even though the analysis is complete, it is not meaningful, so we should it again.

Therefore, I think I will run the analysis again without despacito. So it will become looking at the differences in English Billboard songs. 

```{r include= FALSE}
files_list <- list.files(path = ".", recursive = TRUE,
                         pattern = "*.txt$", full.names = TRUE)
files_list <- files_list[-23]
songs <- lapply(files_list, read_file) %>%
  unlist(.)
```
```{r include= FALSE}
df <- as.data.frame(songs)
corpus_song <- Corpus(VectorSource(df$songs))
```
```{r include= FALSE}
song_words <- corpus_song %>%
  tm_map(removePunctuation)  %>%
  tm_map(removeNumbers)
```
```{r include= FALSE}
dtm <- DocumentTermMatrix(song_words)
```
```{r include= FALSE}
doc_tf <- apply(as.matrix(dtm), 2, function(word) {word/sum(word)})
```
```{r include= FALSE}
idf <- function(doc) {
  return(log2( length(doc) + 1 / nnzero(doc)) )
}
```
```{r include= FALSE}
doc_idf <- apply(as.matrix(dtm), 1, idf)
```
```{r include= FALSE}
docs_tfidf <- doc_tf * doc_idf
```
```{r include= FALSE}
docs_pca <- prcomp(docs_tfidf, scale = T)
```
### New plots
```{r echo = FALSE}
fviz_eig(docs_pca)
fviz_pca_ind(docs_pca, geom.ind = c("point"), col.ind = "cos2")
fviz_pca_var(docs_pca, col.var = "contrib")
fviz_pca_biplot(docs_pca, geom.ind = "point")
```
```{r include= FALSE}
docs_eig <- get_eig(docs_pca)
docs_var <- get_pca_var(docs_pca)
docs_ind <- get_pca_ind(docs_pca)
```
### K means
```{r}
ind_coord2 <- docs_ind$coord[,1:2]
print(ind_coord2)
wss <- c()
for (i in 1:10) {
  wss[i] <- kmeans(ind_coord2, i)$tot.withinss
}
plot(wss, type = "b")
```
```{r echo = FALSE}
km <- kmeans(ind_coord2, 3)
plot(ind_coord2, col = km$cluster)
points(km$centers, col = 1:3, pch = 8, cex = 2)
```


Usher's yea has come out once again as a distinct category. I believe it is because of the unique use of words like gangster and all

This time Robin Thicke's blurred lines was a distinct group of its own. The usage of words appears to be more sexual than the rest of the songs. Probably explaining the difference. 

The rest of the songs in red, are all very different songs. Thus, I am not particularly sure why they are grouped together. 

I suspected that the tf-idf ==0 words are affecting the results but when I tried deleting them, I can't seem to find them at all. I believe the songs seem to vary too much to find meaningful groups to provide any kind of conclusion. 

Thus, the dataset is too small to derive any meaningful conclusions. 