---
title: "week2hw"
output: html_document
---

# Class Assignment 2 
## Lesson 2 - Data visualization

### We will be looking at how to utilise ggplot to quickly generate various graphs.

#### Bar and scatterplot

I had ggplot2 package pre-installed.  
We will utilise the built-in data in R: the Iris dataset.
```{r}
library(ggplot2)
```
```{r}
data("iris")
```
Next we will start looking at our dataset.
```{r}
print(iris)
summary(iris)
str(iris)
complete.cases(iris)
```
So we can see that we have some continuous variables (Petal.width, Sepal.width...) and categorical variables (Species). Therefore, let us try to plot a scatter and bar chart with the data. 
```{r}
ggplot(iris, aes(x = Species, y = Sepal.Length)) + geom_col()
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) + geom_point()
```  

* Now we will do some housekeeping to take out the datasets that we no longer need.
```{r}
remove(iris)
```

* Same process for line graph
```{r}
data("economics")
str(economics)
ggplot(economics, aes(x = date, y = pce)) + geom_point(color = "blue", size = 1)
ggplot(economics, aes(x = pop, y = unemploy)) + geom_line(color = "pink", size = 2)
remove(economics)
```

* Similar process for box plots and multiple line graph.
```{r}
data("txhousing")
str(txhousing)
ggplot(txhousing, aes(x = date, y = listings, group = city, color = city)) + geom_line()
```

* Box plot
```{r}
ggplot(txhousing, aes(x = year, y = sales, group = year)) + geom_boxplot()
```

* Stacked barplot - a bad example, but the code works :')
```{r}
ggplot(txhousing, aes(x = year, fill = city)) + geom_bar(position = "fill")
```

## AND WE HAVE COMPLETED THE EXERCISE. The next exercise is to import data from the internet. 
