---
title: "wordcloud"
output: html_document
---
# Class Assignment 2.2 - Word Cloud
### _Date: 11/7/17_  

#####今天我們要繪製一個文字云，來萃取一些文章的精髓。我選了中國近代傳奇企業家，馬雲的退休演講詞。我們就來一起看看他大概都是在講什麼吧！

#####Today we are going to draw a word cloud to capture the essence of some articles. I chose the modern legendary entrepreneur, Jack Mah's resignation speech. Let us take a look at what he said together!


####開啟R包裹 (Open R packages)
```{r cars}
library(jiebaR)
library(wordcloud2)
library(magrittr)
Sys.setlocale("LC_ALL", locale = "Chinese")
```
####匯入文字切割器函數 (Insert the phrase identifier function)
```{r}
wk <- worker()
```
####匯入文字 (import text)
```{r}
text <- readLines("Mayunspeech1.txt", encoding = "UTF-8")
```
####找出無意義的單字 (Identify meaningless words into a vector)
```{r}
stopwords <- c("我","的","在","和","都","也","不","就","上","为","我们","你们","他们","这","从","是",
               "会","个","有","像","把","其实","了", "谁","所","但", "更", "很","什么", "一","因", "让",
               "好", "每", "多", "得", "当", "将","座", "对", "没", "你","到")
```
####建立清楚單字的二步驟 (Create the two step procedure to rid the meanless words)
先是將stopwords轉成一個長的OR string，這樣如果找到其中一個詞就會被刪掉。接下來就把他套到刪除函數。  
First is to turn stopwords into a long OR string, next is to import the string into the substr() function.
```{r}
stopwords.pattern <- paste0(stopwords, sep = "|", collapse = "") %>%
  substr(1, nchar(.) -1)
```
####消滅計劃開始 (Pull the trigger)
```{r}
text <- gsub(stopwords.pattern, " ", text)
```
####切割機啟動(Activate the slicer)
```{r}
speech <- wk[text]
```
####將詞彙都存到一個資料框 (Save the phrases/words into a dataframe)
```{r}
speech <- as.data.frame(table(speech))
```
####整理一下資料框將出現率最高的排第一 (Order the dataframe such that the most frequent word comes first.)
```{r}
freq <- speech[order(speech$Freq, decreasing = T),]
```
####繪製文字云 (Draw the wordcloud)
```{r}
wordcloud2(freq, size = 1.5, color = "random-light", backgroundColor = "grey")
```

#### Now crack a beer and savour the essence of the resignation speech by the legendary Ali group founder Jack Ma. Truly inspiring.